---
title: "Annie's First Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(mosaic)
library(ggformula)
library(rpart)
library(rpart.plot)
knitr::opts_chunk$set(echo = FALSE)
```


## Introduction

A tutorial is a self-contained document that provides flexible facilities for the user to perform R calculations. In order to be self-contained, the document needs to attach any packages that are to be available to the user. This is usually done in the `setup` chunk (which is near the top of this document).

### A command block

Here's a command block that's all ready for you to use. Try it!

```{r block1, exercise=TRUE}
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("In the formula rain ~ humidity + temperature, which is the *response* variable?", allow_retry = TRUE,
    answer("rain", correct = TRUE, message = "Right! The response variable is always to the left of the tilde."),
    answer("humidity"),
    answer("temperature"),
    answer("none of the above")
  ),
  question("Which of the following is a good choice for making a data graphic involving one quantitative and one categorical variable?",
    answer("gf_jitter", correct = TRUE, message = "Good. gf_point is also a possibility, but overplotting can be a problem."),
    answer("gf_smooth"),
    answer("plot_data"),
    answer("data_plot")
  )
)
```

